RCloud: DevOps for Visual Analysis and Data Science

### 2014-03-21 introduction.tex
yes

% How do people do it today?
Individual data scientists and statisticians usually work on loosely
related problems, and must devise effective ways to share their findings
and move results from exploratory data analysis to automated diagnostics
and reports that are deployed for wider consumption.
They generally rely on a patchwork of resources shared informally,
or at best, through systems that attack individual tasks or functions
in the data analysis workcycle.

% Why does this not work?
There are two problems with the current
practice. First, there are gaps in the workflow:
Exploratory Data Analysis (EDA) is done with one set of tools,
and automated reports and deployments with another. This makes
transferring results from EDA to production slow, expensive, and error-prone.
Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from convenient sharing of
scripts, data sets, data feeds, experiments, annotations, and automated
analyses and recommendations. These features are well beyond what existing
repositories and version control systems provide.

@@

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for ...

% We want our solution to play well with the rest of the ecosystem
R has developed a complex ecosystem of compatible packages, software
tools and other resources. For example there are packages that make
it convenient to execute map-reduce programs, generate web interfaces,

>>>>

% How do people do it today?
Individual data scientists and statisticians usually work on loosely
related problems, and must devise effective ways to share their findings
and move results from exploratory data analysis to automated diagnostics
and reports that are deployed for wider consumption.
They generally rely on a patchwork of resources shared informally,
or at best, through systems that attack individual tasks or functions
in the data analysis workcycle. % might cite information visualization reference model or pirolli/card

% Why does this not work?
There are two problems with the current
practice. First, there are gaps in the workflow:
Exploratory Data Analysis (EDA) is done with one set of tools,
and automated reports and deployments with another. This makes
transferring results between EDA and production (in both directions)
slow, expensive, and error-prone. Coordination is done through
meetings and may take months to implement.

Second, EDA environments often assume a single-developer perspective,
while data scientist teams could greatly benefit from convenient searching
and sharing of scripts, data sets, data feeds, experiments, annotations,
and automated analyses and recommendations. These capabilities have had
tremendous impact on information retrieval in general but are well
beyond what existing visual analytics environments provide, or what
is found in today's repositories and version control systems.

@@

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for data analysis and is well-supported by 
a complex ecosystem of compatible packages, software
tools and other resources. Of importance to us, there are
packages for high performance computing in the cloud,
and for generating web graphics.

% We want our solution to play well with the rest of the ecosystem
